A new metric for automatic discovery of periodic patterns in time series

### 2021-03-01 paper/main.Rmd
application section re-write

@@

## Smart meter application to 8 datasets from energy competition

>>>>

The smart meter data set for eight households in Melbourne has been utilized to see the use of the $wpd_{norm}$ proposed in the paper. The data has been cleaned to be a `tsibble` (@wang2019tsibble) containing half-hourly electricity consumption from Jul-2019 to Dec-2019 for each of the households, which is procured by them by downloading their data from the energy supplier/retailer. Demand data for these households are shown in a linear time scale in \autoref{fig:linear-scale-8}. It is evident from the range of the demand data that these households vary in consumption levels as well as in their temporal patterns. In the left panel of \autoref{fig:linear-scale} (a), the linear representation of the entire time period is shown, whereas in the right panel (b) a particular month is shown and furthermore a week has been highlighted to inspect if there is any daily or weekly periodic patterns in their behavior that is reflected when we zoom into the the linear representation of the time series.
We start by asking if the ranking of the harmonies make sense for the households, then compare households to get more insights of what these rankings imply and if they could be used to remove some non-interesting harmonies. Furthermore, we see if the display of the significant harmonies could be validated by zooming in the linear representation of the time series.

<!-- if we are benefiting by moving from a linear to cyclic representation of time to . -->

_Choosing cyclic granularities of interest and removing clashes_

Let $v_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$. The series $v_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes. We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar. Considering $4$ linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$. We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc. Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior. Thus, $7$ cyclic granularities are considered to be of interest. The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analysed for detecting possible periodicities. The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2020-vo].

 <!-- The paper also shows how the number of harmonies could be identified among  by removing clashes. This section shows how we could refine the search further by only looking at significant harmonies. -->

_Choosing and Ranking harmonies for all households_

_Validating ranks of one household_

_Comparing households_

_Validating patterns from linear display_

This is expected to have an assymmetrical distribution as could be seen in \ref{fig:raw-nqt} and the Normal score transform has been applied to make it more symmetric. Let $v*_{i, t}$ denote the normal-quantile transformed electricity demand for $i^{th}$ household for time period $t$.

# application to 4 households

@@
